---
title: "Dimensionality Reduction - Extra Doublet Filtered"
output: html_notebook
---
```{r message=FALSE, warning=FALSE}
library(Seurat)
```

```{r}
sc <- readRDS("./data/seurat_filter2_umap.RDS")
```

```{r}
PCAPlot(sc, group.by="diffday")
PCAPlot(sc, group.by="individual")
PCAPlot(sc, group.by="exp")
```

Before
```{r}
DimPlot(sc, group.by="diffday")
DimPlot(sc, group.by="diffday", split.by="individual", ncol=4)
DimPlot(sc, group.by="diffday", split.by="exp")
```

```{r}
DimPlot(sc, group.by="individual")
DimPlot(sc, group.by="exp")
DimPlot(sc, group.by="collection")
DimPlot(sc, group.by="sample")
DimPlot(sc, group.by="cd")
```

Stem cell markers
```{r}
FeaturePlot(sc, features="POU5F1")
```

Mesoderm markers TBXT and MIXL1, and cardiac mesoderm marker MESP1
```{r}
FeaturePlot(sc, features=c("TBXT", "MIXL1", "MESP1"))
```

Early cardiomyocyte markers
```{r}
FeaturePlot(sc, features=c("KDR", "ISL1", "GATA4"))
```

Later cardiomyocyte markers
```{r}
FeaturePlot(sc, features=c("NKX2-5", "TBX5", "MEF2C"))
```

Cardiomyocyte myofilament genes
```{r}
FeaturePlot(sc, features=c("TNNT2", "MYH6"))
```

What's the deal with the lower left section? Tons of late-day cells that are not expression the cardiomyocyte markers.  Maybe epicardium?  Looking at an epicardium marker gene
```{r}
FeaturePlot(sc, features="IGF2")
```
Not super convincing, will have to come back to this

Now let's see if we can pick out the stressed/ dying cells
```{r}
FeaturePlot(sc, features="percent.mito")
```

Take a look at one apoptosis marker gene
```{r}
FeaturePlot(sc, features="BAX")
```
Not too helpful

Now let's see in UMAP what the PC's are focusing on
```{r}
FeaturePlot(sc, features="PC_1")
FeaturePlot(sc, features="PC_2")
FeaturePlot(sc, features="PC_3")
FeaturePlot(sc, features="PC_4")
FeaturePlot(sc, features="PC_5")
```

What is PC5 picking up on?
```{r}
VizDimLoadings(sc, dims=5, reduction="pca")
```

Lots of mito on the negative side there, is PC5 negatively correlated with mito counts in general or is this just a special set of genes?
```{r}
FeatureScatter(sc, feature1="percent.mito", feature2="PC_5")
```
PC5 seems like a tentative candidate as a proxy for cell vitality - need to explore this (GSEA?)

PC1 seems like it's picking up on extent of cardiomyocyte differentiation, and note that this also does seem to have some correlation with percent mito
```{r}
FeatureScatter(sc, feature1="percent.mito", feature2="PC_1")
```

Let's verify whether PC1 is picking up on cardiomyocyte differentiation
```{r}
VizDimLoadings(sc, dims=1, reduction="pca")
```