---
title: "Doublet Analysis - Collection Day 1"
output: html_notebook
---
```{r message=FALSE, warning=FALSE}
library(Seurat)
```

# Collection Day 1
Differentiation days 1, 3, and 7
## Round 1
```{r}
dir <- "./collections/e1cd1"
```
### Collection 1
```{r}
scd <- readRDS(paste0(dir, "col1_dub"))
sc <- readRDS(paste0(dir, "col1_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

### Collection 2
```{r}
scd <- readRDS(paste0(dir, "col2_dub"))
sc <- readRDS(paste0(dir, "col2_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

### Collection 3
```{r}
scd <- readRDS(paste0(dir, "col3_dub"))
sc <- readRDS(paste0(dir, "col3_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

### Collection 4
```{r}
scd <- readRDS(paste0(dir, "col4_dub"))
sc <- readRDS(paste0(dir, "col4_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

### Collection 5
```{r}
scd <- readRDS(paste0(dir, "col5_dub"))
sc <- readRDS(paste0(dir, "col5_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

### Collection 6
```{r}
scd <- readRDS(paste0(dir, "col6_dub"))
sc <- readRDS(paste0(dir, "col6_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

## Round 2
```{r}
dir <- "./collections/e2cd1"
```
### Collection 1
```{r}
scd <- readRDS(paste0(dir, "col1_dub"))
sc <- readRDS(paste0(dir, "col1_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

### Collection 2
```{r}
scd <- readRDS(paste0(dir, "col2_dub"))
sc <- readRDS(paste0(dir, "col2_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

### Collection 3
```{r}
scd <- readRDS(paste0(dir, "col3_dub"))
sc <- readRDS(paste0(dir, "col3_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

### Collection 4
```{r}
scd <- readRDS(paste0(dir, "col4_dub"))
sc <- readRDS(paste0(dir, "col4_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

### Collection 5
```{r}
scd <- readRDS(paste0(dir, "col5_dub"))
sc <- readRDS(paste0(dir, "col5_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

### Collection 6
```{r}
scd <- readRDS(paste0(dir, "col6_dub"))
sc <- readRDS(paste0(dir, "col6_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

### Collection 7
```{r}
scd <- readRDS(paste0(dir, "col7_dub"))
sc <- readRDS(paste0(dir, "col7_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

## Round 3
```{r}
dir <- "./collections/e3cd1"
```
### Collection 1
```{r}
scd <- readRDS(paste0(dir, "col1_dub"))
sc <- readRDS(paste0(dir, "col1_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

### Collection 2
```{r}
scd <- readRDS(paste0(dir, "col2_dub"))
sc <- readRDS(paste0(dir, "col2_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

### Collection 3
```{r}
scd <- readRDS(paste0(dir, "col3_dub"))
sc <- readRDS(paste0(dir, "col3_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

### Collection 4
```{r}
scd <- readRDS(paste0(dir, "col4_dub"))
sc <- readRDS(paste0(dir, "col4_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

### Collection 5
```{r}
scd <- readRDS(paste0(dir, "col5_dub"))
sc <- readRDS(paste0(dir, "col5_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```

### Collection 6
```{r}
scd <- readRDS(paste0(dir, "col6_dub"))
sc <- readRDS(paste0(dir, "col6_nodub"))
```
#### Doublets
```{r}
DimPlot(scd, group.by="demux.sng1")
FeaturePlot(scd, features="percent.mito")
```
#### No Doublets 
```{r}
DimPlot(sc, group.by="demux.sng1")
FeaturePlot(sc, features="percent.mito")
```