---
title: "Assessment of Quality Filters"
output:
  html_document:
    df_print: paged
---


```{r include=FALSE}
library(ggplot2)
suppressMessages(library(Seurat))
```

```{r}
sc_no_filt <- readRDS("./collections/e1comb.processed.rds")
DimPlot(sc_no_filt, group.by="diffday")
DimPlot(sc_no_filt, group.by="quality")
```

```{r}
sc_filt <- readRDS("./collections/e1comb_filt.processed.rds")
DimPlot(sc_filt, group.by="diffday")
```

```{r}
FeaturePlot(sc_filt,features="TNNT2")
```

```{r}
FeaturePlot(sc_filt, features="IGF2")
```

```{r}
FeaturePlot(sc_filt, features=c("demux.dbl.prb", "percent.mito"))
```

## Gene Set Enrichment Analysis

What gene sets are the low-quality cells enriched for?
```{r}
qual.enrichment <- read.table("./output/gsea/quality/low/hallmark.txt", skip=3, sep="\t", header=T)
qual.enrichment[qual.enrichment$bonferroni.adjusted<=0.05,]
```

Are there any interesting enrichments in the high-quality cells?
```{r}
qual.enrichment <- read.table("./output/gsea/quality/high/hallmark.txt", skip=3, sep="\t", header=T)
qual.enrichment <- qual.enrichment[order(qual.enrichment$bonferroni.adjusted),]
qual.enrichment[qual.enrichment$bonferroni.adjusted<=0.05,]
```

## Cell Cycle Effects
Does it seem like cell cycle scores are having a large effect on this?  Using Seurat tools
```{r}
s.genes <- cc.genes$s.genes
g2m.genes <- cc.genes$g2m.genes
sc_no_filt <- CellCycleScoring(sc_no_filt, s.features=s.genes, g2m.features=g2m.genes, set.ident=F)
sc_no_filt$CC.Difference <- sc_no_filt$S.Score - sc_no_filt$G2M.Score
```

Does the CC difference (differentiates between cycling and non-cycling cells, but not between stages in the cycle) seem to correspond with the low quality cells? How about G2M?
```{r}
DimPlot(sc_no_filt, group.by="quality")
FeaturePlot(sc_no_filt, features="CC.Difference")
FeaturePlot(sc_no_filt, features="G2M.Score")
```

Looking at this more quantitatively
```{r}
cell.cycle.fx <- data.frame(sc_no_filt$CC.Difference)
colnames(cell.cycle.fx) <- "cc.diff"
cell.cycle.fx$g2m <- sc_no_filt$G2M.Score
cell.cycle.fx$quality <- sc_no_filt$quality
g2m.good <- cell.cycle.fx[cell.cycle.fx$quality==T, "g2m"]
g2m.bad <- cell.cycle.fx[cell.cycle.fx$quality==F, "g2m"]
ccdiff.good <- cell.cycle.fx[cell.cycle.fx$quality==T, "cc.diff"]
ccdiff.bad <- cell.cycle.fx[cell.cycle.fx$quality==F, "cc.diff"]

t.ccdiff <- t.test(ccdiff.good, ccdiff.bad)
t.ccdiff
t.ccdiff$p.value

t.g2m <- t.test(g2m.good, g2m.bad, alternative = "less")
t.g2m
t.g2m$p.value

ggplot(cell.cycle.fx, aes(x=cc.diff, fill=quality)) + geom_density(alpha=.3)
ggplot(cell.cycle.fx, aes(x=g2m, fill=quality)) + geom_density(alpha=.3)
```

Sanity check, is this way more pronounced for, say, percent mito and doublet probability?
```{r}
confounder.fx <- data.frame(sc_no_filt$percent.mito)
colnames(confounder.fx) <- "mito"
confounder.fx$dbl <- sc_no_filt$demux.dbl.prb
confounder.fx$quality <- sc_no_filt$quality
mito.good <- confounder.fx[confounder.fx$quality==T, "mito"]
mito.bad <- confounder.fx[confounder.fx$quality==F, "mito"]
dbl.good <- confounder.fx[confounder.fx$quality==T, "dbl"]
dbl.bad <- confounder.fx[confounder.fx$quality==F, "dbl"]

t.mito <- t.test(mito.good, mito.bad, alternative="less")
t.mito
t.mito$p.value

t.dbl <- t.test(dbl.good, dbl.bad, alternative = "less")
t.dbl
t.dbl$p.value

ggplot(confounder.fx, aes(x=mito, fill=quality)) + geom_density(alpha=.3)
ggplot(confounder.fx, aes(x=dbl, fill=quality)) + geom_density(alpha=.3)
```

## Close-Up CD1Col6
```{r}
col6 <- readRDS("./collections/e1cd1col6")
DimPlot(col6, group.by="diffday")
```

```{r warning=F, message=F}
s.genes <- cc.genes$s.genes
g2m.genes <- cc.genes$g2m.genes
col6_cc <- CellCycleScoring(col6, s.features=s.genes, g2m.features=g2m.genes, set.ident=F)
col6_cc$CC.Difference <- col6_cc$S.Score - col6_cc$G2M.Score
col6_cc <- FindVariableFeatures(col6_cc)
col6_cc <- ScaleData(col6_cc, vars.to.regress = "CC.Difference")
col6_cc <- RunPCA(col6_cc)
col6_cc <- FindNeighbors(col6_cc, reduction = "pca")
col6_cc <- FindClusters(col6_cc)
col6_cc <- RunUMAP(col6_cc, dims=1:10)
```

```{r}
DimPlot(col6_cc, group.by="diffday")
```

If anything, it got bigger.  Does gene set enrichment look any different in this close-up?
```{r}
col6 <- FindClusters(col6)
DimPlot(col6)
```
```{r}
markers <- FindMarkers(col6, ident.1=0)
hiq.markers <- rownames(markers)[markers$avg_logFC<0]
loq.markers <- rownames(markers)[markers$avg_logFC>0]
bg <- rownames(col6)[!rownames(col6) %in% rownames(markers)]
write.table(hiq.markers, file="./data/col6_hiqual_markers.txt", row.names=F, col.names=F, quote=F)
write.table(loq.markers, file="./data/col6_loqual_markers.txt", row.names=F, col.names=F, quote=F)
write.table(bg, file="./data/col6_bg_genes.txt", row.names=F, col.names=F, quote=F)
```

Look at enrichment of the low quality cluster
```{r}
qual.enrichment <- read.table("./output/gsea/col6_quality/low/hallmark.txt", skip=3, sep="\t", header=T)
qual.enrichment <- qual.enrichment[order(qual.enrichment$bonferroni.adjusted),]
qual.enrichment[qual.enrichment$bonferroni.adjusted<=0.05,]
```

No enrichment.  What are the marker genes?
```{r}
loq.markers
```
The HIST group are histone proteins, and MT-denotes a mitochondrial read

Enrichment for the high quality genes?
```{r}
qual.enrichment <- read.table("./output/gsea/col6_quality/high/hallmark.txt", skip=3, sep="\t", header=T)
qual.enrichment <- qual.enrichment[order(qual.enrichment$bonferroni.adjusted),]
qual.enrichment[qual.enrichment$bonferroni.adjusted<=0.05,]
```

## Close-Up CD3Col4
```{r}
col4 <- readRDS("./collections/e1cd3col4")
DimPlot(col4, group.by="diffday")
```

Maybe that day 0 arc is what's driving the observed cell-cycle effects
```{r}
s.genes <- cc.genes$s.genes
g2m.genes <- cc.genes$g2m.genes
col4 <- CellCycleScoring(col4, s.features=s.genes, g2m.features=g2m.genes, set.ident=F)
col4$CC.Difference <- col4$S.Score - col4$G2M.Score
FeaturePlot(col4, features="CC.Difference")
FeaturePlot(col4, features="G2M.Score")
```

Maybe not.  Due diligence
```{r}
cell.cycle.fx <- data.frame(col4$CC.Difference)
colnames(cell.cycle.fx) <- "cc.diff"
cell.cycle.fx$g2m <- col4$G2M.Score
cell.cycle.fx$clust <- col4$seurat_clusters != 4
g2m.good <- cell.cycle.fx[cell.cycle.fx$clust==T, "g2m"]
g2m.bad <- cell.cycle.fx[cell.cycle.fx$clust==F, "g2m"]
ccdiff.good <- cell.cycle.fx[cell.cycle.fx$clust==T, "cc.diff"]
ccdiff.bad <- cell.cycle.fx[cell.cycle.fx$clust==F, "cc.diff"]

t.ccdiff <- t.test(ccdiff.good, ccdiff.bad)
t.ccdiff
t.ccdiff$p.value

t.g2m <- t.test(g2m.good, g2m.bad, alternative = "less")
t.g2m
t.g2m$p.value

ggplot(cell.cycle.fx, aes(x=cc.diff, fill=clust)) + geom_density(alpha=.3)
ggplot(cell.cycle.fx, aes(x=g2m, fill=clust)) + geom_density(alpha=.3)
```

GSEA
```{r eval=FALSE}
Idents(col4) <- col4$seurat_clusters
markers <- FindMarkers(col4, ident.1=4)
hiq.markers <- rownames(markers)[markers$avg_logFC<0]
loq.markers <- rownames(markers)[markers$avg_logFC>0]
bg <- rownames(col4)[!rownames(col4) %in% rownames(markers)]
write.table(hiq.markers, file="../data/col4_hiqual_markers.txt", row.names=F, col.names=F, quote=F)
write.table(loq.markers, file="../data/col4_loqual_markers.txt", row.names=F, col.names=F, quote=F)
write.table(bg, file="../data/col4_bg_genes.txt", row.names=F, col.names=F, quote=F)
```

```{r}
qual.enrichment <- read.table("./output/gsea/cd3col4/low/sc.txt", skip=3, sep="\t", header=T)
qual.enrichment <- qual.enrichment[order(qual.enrichment$bonferroni.adjusted),]
qual.enrichment[qual.enrichment$bonferroni.adjusted<=0.05,]
```

Bingo! Does using Seurat's regression tools help get rid of this?
```{r warning=F, message=F}
col4_cc <- FindVariableFeatures(col4)
col4_cc <- ScaleData(col4_cc, vars.to.regress = "CC.Difference")
col4_cc <- RunPCA(col4_cc)
col4_cc <- FindNeighbors(col4_cc, reduction = "pca")
col4_cc <- FindClusters(col4_cc)
col4_cc <- RunUMAP(col4_cc, dims=1:10)
DimPlot(col4_cc, group.by="diffday")
```

Nope, how about just regressing out G2M score
```{r warning=F, message=F}
col4_cc <- FindVariableFeatures(col4)
col4_cc <- ScaleData(col4_cc, vars.to.regress = c("G2M.Score"))
col4_cc <- RunPCA(col4_cc)
col4_cc <- FindNeighbors(col4_cc, reduction = "pca")
col4_cc <- FindClusters(col4_cc)
col4_cc <- RunUMAP(col4_cc, dims=1:10)
DimPlot(col4_cc, group.by="diffday")
```

No - this just doesn't seem to be working.  But I expect the enrichment for G2M markers stems from these arcs, which appear in each collection on collection day 3 (makes sense, we're mixing highly proliferative iPSCs and cardiomyocytes)