---
title: "Quality Control"
output:
  html_document:
    df_print: paged
---

This notebook runs through some checks for quality control of the sequencing and Demuxlet (cell assignment) results.  Seurat object construction based on the pipeline created by Reem Elorbany [here](https://relorbany.github.io/Exp1_prelim_analysis/scCM_round1_lowpass_combined.html).

<!-- Note that in order to run this notebook in R, you will need to set the working directory to the parent of the analytics folder, not the analytics folder itself (ie, open the file, set working directory to file, and then run setwd("../") -->

First, we load necessary libraries and pull the data that file saved

```{r include=FALSE}
library(ggplot2)
library(ggridges)
suppressMessages(library(Seurat))
```

```{r load_data}
demux1 <- readRDS("./data/demux_exp1.RDS")
demux2 <- readRDS("./data/demux_exp2.RDS")
demux3 <- readRDS("./data/demux_exp3.RDS")
```

Take a look at assignments per collection

```{r demuxlet-exp1}
ggplot(demux1, aes(x = collection, y = counts, fill = assignment)) + 
  geom_bar(stat = 'identity', position = 'stack') + 
  facet_grid(~colday) + ggtitle("Round 1 of Collections")
```

```{r demuxlet-exp2}
ggplot(demux2, aes(x = collection, y = counts, fill = assignment)) + 
  geom_bar(stat = 'identity', position = 'stack') + 
  facet_grid(~colday) + ggtitle("Round 2 of Collections")
```

```{r demuxlet-exp3}
ggplot(demux3, aes(x = collection, y = counts, fill = assignment)) + 
  geom_bar(stat = 'identity', position = 'stack') + 
  facet_grid(~colday) + ggtitle("Round 3 of Collections")
```

Now we're going to take a look at some other qc metrics
```{r}
sc1 <- readRDS("./data/seurat_round1_allsinglets.RDS")
sc2 <- readRDS("./data/seurat_round2_allsinglets.RDS")
sc3 <- readRDS("./data/seurat_round3_allsinglets.RDS")
```

Let's take a look at the distributions of the read counts 
```{r}
exp1 <- cbind(data.frame(sc1$nCount_RNA), c(data.frame(sc1$nFeature_RNA, data.frame(sc1$percent.mito), data.frame(sc1$diffday), data.frame(sc1$individual))))
exp2 <- cbind(data.frame(sc2$nCount_RNA), c(data.frame(sc2$nFeature_RNA, data.frame(sc2$percent.mito), data.frame(sc2$diffday), data.frame(sc2$individual))))
exp3 <- cbind(data.frame(sc3$nCount_RNA), c(data.frame(sc3$nFeature_RNA), data.frame(sc3$percent.mito), data.frame(sc3$diffday), data.frame(sc3$individual)))
```

I'll also make a combined df
```{r}
colnames(exp1) <- c("nCount_RNA", "nFeature_RNA", "percent.mito", "diffday", "individual")
exp1$exp <- rep(1, nrow(exp1))
colnames(exp2) <- c("nCount_RNA", "nFeature_RNA", "percent.mito", "diffday", "individual")
exp2$exp <- rep(2, nrow(exp2))
colnames(exp3) <- c("nCount_RNA", "nFeature_RNA", "percent.mito", "diffday", "individual")
exp3$exp <- rep(3, nrow(exp3))
exp123 <- rbind(exp1, exp2, exp3)
```


With this we can create our plots

Quality control for all three rounds of experiments combined (19 individuals)
```{r message=FALSE, warning=FALSE}
max.98 <- quantile(exp123$nCount_RNA, 0.98)
ggplot(exp123, aes(x = nCount_RNA, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  ggtitle("Read counts by individual (all)")

ggplot(exp123, aes(x = nCount_RNA, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  facet_grid(~diffday)+
  ggtitle("Read counts by individual, separated by diffday (all)")

max.98 <- quantile(exp123$nCount_RNA, 0.98)
ggplot(exp123, aes(x = nCount_RNA, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  ggtitle("Read counts by diffday (all)")

ggplot(exp123, aes(x = nCount_RNA, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  facet_grid(~individual) +
  ggtitle("Read counts by diffday, separated by individual (all)")

max.98 <- quantile(exp123$nFeature_RNA, 0.98)
ggplot(exp123, aes(x = nFeature_RNA, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  ggtitle("Gene counts by individual (all)")

ggplot(exp123, aes(x = nFeature_RNA, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  facet_grid(~diffday) +
  ggtitle("Gene counts by individual, separated by diffday (all)")

max.98 <- quantile(exp123$nFeature_RNA, 0.98)
ggplot(exp123, aes(x = nFeature_RNA, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  ggtitle("Gene counts by diffday (all)")

ggplot(exp123, aes(x = nFeature_RNA, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  facet_grid(~individual) +
  ggtitle("Gene counts by diffday, separated by individual (all)")

ggplot(exp123, aes(x = percent.mito, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, 100), breaks=seq(0, 100, 20)) +
  ggtitle("Mito counts by individual (all)")

ggplot(exp123, aes(x = percent.mito, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, 100), breaks=seq(0, 100, 50)) +
  facet_grid(~diffday) +
  ggtitle("Mito counts by individual, separated by diffday (all)")

ggplot(exp123, aes(x = percent.mito, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, 100), breaks=seq(0, 100, 20)) +
  ggtitle("Mito counts by diffday (all)")

ggplot(exp123, aes(x = percent.mito, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, 100), breaks=seq(0, 100, 50)) +
  facet_grid(~individual) +
  ggtitle("Mito counts by diffday, separated by individual (all)")

```
Quality control for exclusively the first round of experiments (6 individuals)
```{r message=FALSE, warning=FALSE}
max.98 <- quantile(exp1$nCount_RNA, 0.98)
ggplot(exp1, aes(x = nCount_RNA, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98))+
  ggtitle("Read counts by individual (round 1)")

ggplot(exp1, aes(x = nCount_RNA, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  facet_grid(~diffday) +
  ggtitle("Read counts by individual, separated by diffday (round 1)")

max.98 <- quantile(exp1$nCount_RNA, 0.98)
ggplot(exp1, aes(x = nCount_RNA, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  ggtitle("Read counts by diffday (round 1)")

ggplot(exp1, aes(x = nCount_RNA, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  facet_grid(~individual) +
  ggtitle("Read counts by diffday, separated by individual (round 1)")

max.98 <- quantile(exp1$nFeature_RNA, 0.98)
ggplot(exp1, aes(x = nFeature_RNA, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  ggtitle("Gene counts by individual (round 1)")

ggplot(exp1, aes(x = nFeature_RNA, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  facet_grid(~diffday) +
  ggtitle("Gene counts by individual, separated by diffday (round 1)")

max.98 <- quantile(exp1$nFeature_RNA, 0.98)
ggplot(exp1, aes(x = nFeature_RNA, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  ggtitle("Gene counts by diffday (round 1)")

ggplot(exp1, aes(x = nFeature_RNA, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  facet_grid(~individual) + 
  ggtitle("Gene counts by diffday, separated by individual (round 1)")

ggplot(exp1, aes(x = percent.mito, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, 100), breaks=seq(0, 100, 20)) +
  ggtitle("Mito counts by individual (round 1)")

ggplot(exp1, aes(x = percent.mito, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, 100), breaks=seq(0, 100, 50)) +
  facet_grid(~diffday) +
  ggtitle("Mito counts by individual, separated by diffday (round 1)")

ggplot(exp1, aes(x = percent.mito, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, 100), breaks=seq(0, 100, 20)) +
  ggtitle("Mito counts by diffday (round 1)")

ggplot(exp1, aes(x = percent.mito, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, 100), breaks=seq(0, 100, 50)) +
  facet_grid(~individual) +
  ggtitle("Mito counts by diffday, separated by individual (round 1)")
```

Quality Control for Round 2
```{r message=FALSE, warning=FALSE}
max.98 <- quantile(exp2$nCount_RNA, 0.98)
ggplot(exp2, aes(x = nCount_RNA, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98))+
  ggtitle("Read counts by individual (round 2)")

ggplot(exp2, aes(x = nCount_RNA, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  facet_grid(~diffday) +
  ggtitle("Read counts by individual, separated by diffday (round 2)")

max.98 <- quantile(exp2$nCount_RNA, 0.98)
ggplot(exp2, aes(x = nCount_RNA, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  ggtitle("Read counts by diffday (round 2)")

ggplot(exp2, aes(x = nCount_RNA, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  facet_grid(~individual) +
  ggtitle("Read counts by diffday, separated by individual (round 2)")

max.98 <- quantile(exp2$nFeature_RNA, 0.98)
ggplot(exp2, aes(x = nFeature_RNA, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  ggtitle("Gene counts by individual (round 2)")

ggplot(exp2, aes(x = nFeature_RNA, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  facet_grid(~diffday) +
  ggtitle("Gene counts by individual, separated by diffday (round 2)")

max.98 <- quantile(exp2$nFeature_RNA, 0.98)
ggplot(exp2, aes(x = nFeature_RNA, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  ggtitle("Gene counts by diffday (round 2)")

ggplot(exp2, aes(x = nFeature_RNA, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  facet_grid(~individual) +
  ggtitle("Gene counts by diffday, separated by individual (round 2)")

ggplot(exp2, aes(x = percent.mito, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, 100), breaks=seq(0, 100, 20)) +
  ggtitle("Mito counts by individual (round 2)")

ggplot(exp2, aes(x = percent.mito, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, 100), breaks=seq(0, 100, 50)) +
  facet_grid(~diffday) +
  ggtitle("Mito counts by individual, separated by diffday (round 2)")

ggplot(exp2, aes(x = percent.mito, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, 100), breaks=seq(0, 100, 20)) +
  ggtitle("Mito counts by diffday (round 2)")

ggplot(exp2, aes(x = percent.mito, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, 100), breaks=seq(0, 100, 50)) +
  facet_grid(~individual) +
  ggtitle("Mito counts by diffday, separated by individual (round 2)")
```

Quality Control for Round 3
```{r message=FALSE, warning=FALSE}
max.98 <- quantile(exp3$nCount_RNA, 0.98)
ggplot(exp3, aes(x = nCount_RNA, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  ggtitle("Read counts by individual (round 3)")

ggplot(exp3, aes(x = nCount_RNA, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  facet_grid(~diffday) +
  ggtitle("Read counts by individual, separated by diffday (round 3)")

max.98 <- quantile(exp3$nCount_RNA, 0.98)
ggplot(exp3, aes(x = nCount_RNA, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  ggtitle("Read counts by diffday (round 3)")

ggplot(exp3, aes(x = nCount_RNA, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  facet_grid(~individual) +
  ggtitle("Read counts by diffday, separated by individual (round 3)")

max.98 <- quantile(exp3$nFeature_RNA, 0.98)
ggplot(exp3, aes(x = nFeature_RNA, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  ggtitle("Gene counts by individual (round 3)")

ggplot(exp3, aes(x = nFeature_RNA, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  facet_grid(~diffday) +
  ggtitle("Gene counts by individual, separated by diffday (round 3)")

max.98 <- quantile(exp3$nFeature_RNA, 0.98)
ggplot(exp3, aes(x = nFeature_RNA, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  ggtitle("Gene counts by diffday (round 3)")

ggplot(exp3, aes(x = nFeature_RNA, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, max.98), breaks=seq(0, max.98, max.98)) +
  facet_grid(~individual) +
  ggtitle("Gene counts by diffday, separated by individual (round 3)")

max.98 <- quantile(exp3$percent.mito, 0.98)
ggplot(exp3, aes(x = percent.mito, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, 100), breaks=seq(0, 100, 20)) +
  ggtitle("Mito counts by individual (round 3)")

ggplot(exp3, aes(x = percent.mito, y = individual, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, 100), breaks=seq(0, 100, 50)) +
  facet_grid(~diffday) +
  ggtitle("Mito counts by individual, separated by diffday (round 3)")

ggplot(exp3, aes(x = percent.mito, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, 100), breaks=seq(0, 100, 20)) +
  ggtitle("Mito counts by diffday (round 3)")

ggplot(exp3, aes(x = percent.mito, y = diffday, height=..density..)) +
  geom_density_ridges() +
  scale_x_continuous(limits = c(0, 100), breaks=seq(0, 100, 50)) +
  facet_grid(~individual) +
  ggtitle("Mito counts by diffday, separated by individual (round 3)")

```
